---
title: "Introduction to Data Science - Homework"
author: "Milous Loche - `mloche1355@floridapoly.edu`"
output: html_notebook
---


# Problem 1 

Load the `tidyverse` package

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

> In this problem you will work with vehicle fuel economy data from the US EPA (Environmental Protection Agency), ranging from 1985-2015. 

Read the data using the code below:

```{r, message=FALSE, warning=FALSE}
vehicles <- read_csv("https://raw.githubusercontent.com/reisanar/datasets/master/vehicles.csv")
```

   Variable  | Description
-------------|-----------------------------------------
`id`         | Unique EPA identifier
`make`       | Manufacturer
`model`      | Model name
`year`       | Model year
`class`      | EPA vehicle size class
`trans`      | Transmission
`drive`      | Drive train
`cyl`        | Number of cylinders
`displ`      | Engine displacement, in litres
`fuel`       | Fuel type
`hwy`        | Highway fuel economy, in mpg
`cty`        | City fuel economy, in mpg


(a) (6 points) **Select** the different manufacturers (makes) of the cars in this data set. Save this vector in a variable called `makes`

```{r}
# Solution for 1A:
makes <- select(vehicles, make)
```


(b) (6 points) Can you determine **how many different car manufacturers** are represented by the data set?

```{r}
# Solution for 1B:
count(makes)
```


(c) (6 points) **Filter** the data set for vehicles manufactured in 1998.

```{r}
# Solution for 1C:
filter(vehicles, year == 1998)
```


(d) (6 points) **Mutate** the 1998 cars data frame to add a column `average` that has the average gas mileage (between city and highway MPG) for each car

```{r}
# Solution for 1D:
vehicles <- mutate(vehicles, average = (hwy + cty) / 2)
```


(e) (6 points) Of all vehicles, what is the vehicle ID of the vehicle with the worst highway MPG?

```{r}
# Solution for 1E:
vehicles %>%
  arrange(-average)
  
```



(f) (6 points) Which 2013 Acura model has the best highway MPG? Which 2015 Honda model has the best highway MPG?

```{r}
# Solution for 1F:

  two13 <- filter(vehicles, make == "Acura", year == 2013)

  
```


(g) (6 points) Create a **data visualization** of your choice using this dataset. Comment on the results.

```{r}
# Solution for 1G:

```


# Problem 2

Load the `nycflights13` package. 

```{r}
library(nycflights13)
```


> Use the `flights` dataframe to answer the following questions. 

(a) (6 points) Find all flights headed to MCO, and **select** only the origin, destination, and the departure time.

```{r}
# Solution for 2A:

```


(b) (6 points) Consider flights from JFK to TPA. What was the **average, minimum, and maximum** _air time_ of those flights? 

```{r}
# Solution for 2B:

```


(c) (6 points) What was the **average departure delay** in each month? Save this as a data frame `dep_delay_by_month`. (Hint: you may have to perform a grouping operation then summarizing your data).

```{r}
# Solution for 2C:

```


(d) (8 points) Which month had the **largest average departure delay**?

```{r}
# Solution for 2D:

```


(e) (8 points) To which destinations were the **average arrival delays the highest**?

```{r}
# Solution for 2E:

```


(f) (6 points) Which airline had the **smallest average arrival delay**?

```{r}
# Solution for 2F:

```


(g) (6 points) Find all flights that were operated by United, American, or Delta.

```{r}
# Solution for 2G:

```


(h) (6 points) Find all the flights (if any) headed to Orlando, Tampa, or Miami with a scheduled departure time later than 8:00 PM.

```{r}
# Solution for 2H:

```


(i) (6 points) Create a **data visualization** of your choice using this dataset. Comment on the results.

```{r}
# Solution for 2I:

```






